% !TeX TS-program = lualatex
% !TeX encoding = UTF-8
%
% File novel.tex, part of `novel' LuaLaTeX document class.
% Copyright 2024 Robert Allgeyer.
% This file may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, version 1.3c.
% License URL:  https://www.latex-project.org/lppl/lppl-1-3c/

% SOURCE CODE FOR FILE novel.pdf, the cover info for `novel' document class.
% IF YOU COMPILE THIS DOCUMENT: Be sure that both this file and
%   novel.pdf (if present) have read/write permissions for any user.
%   Otherwise, compile may fail at the point where files are written.

\documentclass{novel} % v. 2.1.
% Almost all settings are defaults.
\SetHeadFootStyle{3}
\SetTitle{Novel Document Class} % only footer, with page number
% The following PDF/X standard is typical for USA print-on-demand.
% However, not every P.O.D. service needs PDF/X these days.
\SetPDFX[CGATSTR001]{X-1a:2001}
\begin{document}
\thispagestyle{empty}
\begin{ChapterStart}[8]
\vspace{\nbs} % \nbs is normal baselineskip
\ChapterTitle{NOVEL}
\vspace{\nbs}
\ChapterSubtitle{A Document Class for the Rest of Us}
{\centering Version 2.0.1 (February 2024)\par}
\end{ChapterStart}

\textbf{Where is the documentation??} It is HTML.\\
(texroot)/doc/lualatex/novel/novel-documentation.html.

\scenebreak

\textbf{News:} This document class was first privately used in 2014.
Then, in 2018, it was improved, documented, and released. It has been
maintained through TeXlive 2023. It is expected to work in the future, but is
no longer maintained by its original creator.\par
Changes in print-on-demand technology have made many parts of this code
irrelevant. There are also a few commands that require graphic design
experience for proper usage. And a few settings, which should be simple and
obvious, are complex and arcane.\par
If \emph{novel} works for you, good. But if you are simply writing a fiction
novel, nothing fancy, then see if CTAN and TeXlive have a package named
\emph{novelette}. As of late January 2024, the package is in beta test
(not released yet). If the package exists and can be installed, then you
should prefer \emph{novelette}. 

\scenebreak

\textbf{Description:} The \emph{novel} document class is for writers of
original fiction, to be printed to paper, with attention to the requirements
of the print-on-demand market. Non-color interiors and color covers are
supported. Images are supported, but only as they might be used in fiction,
not picture books.

If your work is an E-book, or uses interior color other than gray, or is
academic, then this document class is not for you. 

But if you are writing a detective novel, or science fiction, or a collection
of short stories, then you are in the right place.

\makeatletter\nocle@rtoendtrue\makeatother % For developer only.
\end{document}







